paper1-INTERACT-analysis

### 2023-10-12 paper1-INTERACT-analysis.Rmd
Update objective 2 to run on valid wear days (sd_valid)

Read in SD TOP: 
```{r,results="hide"}
  sd_pa<-read.csv("sensdoc-wearing-2023.csv") # 5575
```

@@

  ggsave(si_plot,file="figures//figure4.pdf",width=5.5,height=3.25)
  ggsave(si_plot,file="submission to IJE//figure4.pdf",width=175,height=95,unit="mm") # for IJBNPA
```

@@

*Columns 5 and 6: valid participant-days from wave 2, stratified by stringency index (sd_valid)*: 
CLEAR imbalances of gender, age, kids, education and employment status (not income)
```{r, echo=FALSE}
  balance_by_SI_full<-CreateTableOne(vars=c(#"mean_wave_mvpa","mean_wave_wear",
                                        "wear","mean_mvpa_sd","mean_temp","total_precip",
                                        "city_id","gender","age_cat","income",
                                        "children","education","employment"),
                                 strata="si_cat",
                                 data=sd_valid,test=FALSE,
                                 includeNA=TRUE)
  kableone(balance_by_SI_full)
  #print(kableone(balance_by_SI_full,quote=TRUE,noSpaces=TRUE))
```

@@

  ggsave(figure1,file="figures//figure1.pdf",width=6,height=4)
  ggsave(figure1,file="submission to IJE//figure1.pdf",width=175,height=100,unit="mm")
```

@@

  figure2<-ggplot(sd_valid[sd_valid$wave_id=="wave 1",],aes(x=doy3,y=mean_mvpa_sd,color=wave_id)) +
                          geom_point(alpha=0.15,size=1)+
                          geom_point(data=sd_valid[sd_valid$wave_id=="wave 2",],aes(x=doy3,y=mean_mvpa_sd),
                                     alpha=0.15,size=1) +
                          scale_colour_manual(values=c("wave 1"="grey65",
                                                       "wave 2"="black"),
                                              labels=c("Wave 1 (2018-2019)","Wave 2 (2020-2021)")) +
                          geom_smooth(method=lm)+
                          geom_smooth(data=sd_valid[sd_valid$wave_id=="wave 2",],aes(x=doy3,y=mean_mvpa_sd),method=lm) +
                          theme_classic()+
                          labs(#title = "Daily minutes of moderate-to-vigorous physical activity by day of the year: ", # removing title for IJBNPA
                               #subtitle = "Wave 1 (2018-2019) vs. Wave 2 (2020-2021)",
                               y = "Daily minutes of moderate-to-vigorous physical activity",
                               x = "Date")+
                          guides(color=guide_legend("")) +
                          theme(axis.title = element_text(face="bold",size=10),
                                axis.text.x = element_text(angle=90,vjust = 0.5, hjust=1,size=8),
                                axis.text.y = element_text(size=8),
                                plot.title = element_text(face="bold",hjust=0.5,size=10),
                                plot.subtitle = element_text(hjust=0.5,size=10),
                                legend.position="bottom",
                                legend.key.size = unit(1,"line"),
                                legend.spacing.x = unit(0.25, 'cm'),
                                legend.margin=margin(-3, 0, 0, 0),
                                legend.text = element_text(size=8,margin = margin(r = 0.4, unit = 'cm'))) 
  figure2
  ggsave(figure2,file="figure2.pdf",width=6,height=4)
  ggsave(figure2,file="submission to IJE//figure2.pdf",width=175,height=120,unit="mm")
```

@@

**Create income plot**
```{r,echo=FALSE,results=FALSE,warning=FALSE}
# Add a income-wave interaction term to the adjusted model  
income_covar_valid_final<-glmer.nb(mean_mvpa_sd~ wave_id + city_id + wave_id*income + wearRS +
                                                age_cat + employment + income +
                                                mean_temp + total_precip + 
                                                (1|interact_id),
                          data=sd_valid[sd_valid$age_cat!="missing",])

@@

**Create education plot**
```{r,echo=FALSE,results=FALSE,warning=FALSE}
# Add a education-wave interaction term to the adjusted model 
education_covar_valid_final<-glmer.nb(mean_mvpa_sd~ wave_id + city_id + wave_id*education + wearRS +
                                                age_cat + employment + income + education +
                                                mean_temp + total_precip + 
                                                (1|interact_id),
                          data=sd_valid[sd_valid$age_cat!="missing" & sd_valid$education!="don't know/prefer not to answer",])

@@

**Create employment figure**
```{r,echo=FALSE,results=FALSE,warning=FALSE}
# Add an employment status-wave interaction term to the adjusted model 
employment_covar_valid_final<-glmer.nb(mean_mvpa_sd~ wave_id + city_id + wave_id*employment + wearRS +
                                                age_cat + education + income + employment +
                                                mean_temp + total_precip + 
                                                (1|interact_id),
                          data=sd_valid[sd_valid$age_cat!="missing",])

@@

em_figures<-grid.arrange(income_Plot.HandPick,
                         employment_Plot.HandPick,
                         education_Plot.HandPick,
            left=titleY,
            widths=c(1,1,1),
            heights=c(1),
            nrow=1)
ggsave(em_figures,file="figures//figure3.jpeg",width=175,height=85,units="mm")
ggsave(em_figures,file="figures//figure3.pdf",width=175,height=85,units="mm")
ggsave(em_figures,file="submission to IJE//figure3.pdf",width=175,height=85,units="mm")
```

@@

#### Unadjusted model (row 1 table 3)
```{r,echo=FALSE,result=FALSE,warning=FALSE}
  length(sd_pa[sd_pa$wave_id=="wave 2",]$interact_id) # missing 7 observations???
  length(sd_pa[is.na(sd_pa$stringencyIndex) & sd_pa$wave_id=="wave 2",]$interact_id)
```

**Model**
```{r,warning=FALSE}
# model is missing 7 observations from wave 2?
  si_all_unadj<-glmer.nb(mean_mvpa_sd~ stringencyIndex + (1|interact_id),
                         data=sd_pa[sd_pa$wave_id=="wave 2",]) 
  summary(si_all_unadj)
```

@@

**Model**
```{r,warning=FALSE}
  si_all_cov_fully<-glmer.nb(mean_mvpa_sd~ stringencyIndex + wear + city_id + 
                          mean_temp + total_precip + 
                          age_cat + 
                          gender + 
                          children + 
                          employment + 
                          (1|interact_id),
                          data=sd_pa[sd_pa$gender!="other" & sd_pa$age_cat!="missing" &
                                     sd_pa$wave_id=="wave 2",])
  summary(si_all_cov_fully)
```

@@

*Objective 1*

@@

Unadjusted model (all person-days with 600+ minutes of wear time)
```{r}
length(sd_valid$date)
table(sd_valid$wave_id)
```
Adjusted model (complete case; no missing data for confounders)
```{r}
# models adjusted for wave_id + city_id + wearRS + age_cat + employment + income + mean_temp + total_precip -- no missing data for wave_id, city_id, employment status, income... look for number of missing for each of the remaining variables

@@

*Sensitivity analysis 1*

@@

Adjusted
```{r}
print("age")
summary(sd_valid_both$age_cat)

print("mean_temp")
summary(sd_valid_both$mean_temp)

print("total_precip")
summary(sd_valid_both$total_precip)
```
*Sensitivity analysis 2*

@@

Adjusted
```{r}
print("age")
summary(sens_valid$age_cat) # don't need to check for missingness in weather data since we aren't controlling for weather in this model
```

*Objective 2*

@@

Adjusted model (complete case; no missing data for confounders)
```{r}
print("age")
summary(sd_valid[sd_valid$wave_id=="wave 2",]$mean_temp)
```

>>>>

Read in SD TOP: 
```{r,results="hide"}
  sd_pa<-read.csv("Data//final-for-analysis//sensdoc-wearing-2023.csv") # 5575
```

@@

  ggsave(si_plot,file="figures//figure4.png",width=5.5,height=3.25)
  ggsave(si_plot,file="submission to IJE//figure4.png",width=175,height=95,unit="mm") # for IJBNPA
```

@@

*Columns 5, 6 and 7: valid participant-days from wave 2, stratified by stringency index (sd_valid)*: 
CLEAR imbalances of gender, age, kids, education and employment status (not income)
```{r, echo=FALSE}
  balance_by_SI_full<-CreateTableOne(vars=c(#"mean_wave_mvpa","mean_wave_wear",
                                        "wear","mean_mvpa_sd","mean_temp","total_precip",
                                        "city_id","gender","age_cat","income",
                                        "children","education","employment"),
                                 strata="si_cat",
                                 data=sd_valid,test=FALSE,
                                 includeNA=TRUE)
  kableone(balance_by_SI_full)
  #print(kableone(balance_by_SI_full,quote=TRUE,noSpaces=TRUE))
```

@@

  ggsave(figure1,file="figures//figure1.png",width=6,height=4)
  ggsave(figure1,file="submission to IJE//figure1.png",width=175,height=100,unit="mm")
```

@@

  figure2<-ggplot(sd_valid[sd_valid$wave_id=="wave 1",],aes(x=doy3,y=mean_mvpa_sd,color=wave_id)) +
                          geom_point(alpha=0.15,size=1)+
                          geom_point(data=sd_valid[sd_valid$wave_id=="wave 2",],aes(x=doy3,y=mean_mvpa_sd),
                                     alpha=0.15,size=1) +
                          scale_colour_manual(values=c("wave 1"="grey65",
                                                       "wave 2"="black"),
                                              labels=c("Wave 1 (2018-2019)","Wave 2 (2020-2021)")) +
                          geom_smooth(method=lm)+
                          geom_smooth(data=sd_valid[sd_valid$wave_id=="wave 2",],aes(x=doy3,y=mean_mvpa_sd),method=lm) +
                          theme_classic()+
                          labs(#title = "Daily minutes of moderate-to-vigorous physical activity by day of the year: ", # removing title for IJBNPA
                               #subtitle = "Wave 1 (2018-2019) vs. Wave 2 (2020-2021)",
                               y = "Daily minutes of moderate-to-vigorous physical activity",
                               x = "Date")+
                          guides(color=guide_legend("")) +
                          theme(axis.title = element_text(face="bold",size=10),
                                axis.text.x = element_text(angle=90,vjust = 0.5, hjust=1,size=8),
                                axis.text.y = element_text(size=8),
                                plot.title = element_text(face="bold",hjust=0.5,size=10),
                                plot.subtitle = element_text(hjust=0.5,size=10),
                                legend.position="bottom",
                                legend.key.size = unit(1,"line"),
                                legend.spacing.x = unit(0.25, 'cm'),
                                legend.margin=margin(-3, 0, 0, 0),
                                legend.text = element_text(size=8,margin = margin(r = 0.4, unit = 'cm'))) 
  figure2
  ggsave(figure2,file="figure2.png",width=6,height=4)
  ggsave(figure2,file="submission to IJE//figure2.png",width=175,height=120,unit="mm")
```

@@

```{r,echo=FALSE,results=FALSE,warning=FALSE}
# income plot

# Add a income-wave interaction term to the adjusted model  
income_covar_valid_final<-glmer.nb(mean_mvpa_sd~ wave_id + city_id + wave_id*income + wearRS +
                                                age_cat + employment + income +
                                                mean_temp + total_precip + 
                                                (1|interact_id),
                          data=sd_valid[sd_valid$age_cat!="missing",])

@@

```{r,echo=FALSE,results=FALSE,warning=FALSE}
# education plot

# Add a education-wave interaction term to the adjusted model 
education_covar_valid_final<-glmer.nb(mean_mvpa_sd~ wave_id + city_id + wave_id*education + wearRS +
                                                age_cat + employment + income + education +
                                                mean_temp + total_precip + 
                                                (1|interact_id),
                          data=sd_valid[sd_valid$age_cat!="missing" & sd_valid$education!="don't know/prefer not to answer",])

@@

```{r,echo=FALSE,results=FALSE,warning=FALSE}
# employment plot

# Add an employment status-wave interaction term to the adjusted model 
employment_covar_valid_final<-glmer.nb(mean_mvpa_sd~ wave_id + city_id + wave_id*employment + wearRS +
                                                age_cat + education + income + employment +
                                                mean_temp + total_precip + 
                                                (1|interact_id),
                          data=sd_valid[sd_valid$age_cat!="missing",])

@@

em_figures<-grid.arrange(income_Plot.HandPick,
                         employment_Plot.HandPick,
                         education_Plot.HandPick,
            left=titleY,
            widths=c(1,1,1),
            heights=c(1),
            nrow=1)
ggsave(em_figures,file="figures//figure3.png",width=175,height=85,units="mm")
ggsave(em_figures,file="submission to IJE//figure3.png",width=175,height=85,units="mm")
```

@@

#### Unadjusted model (row 1 table 3)

**Model**
```{r,warning=FALSE}
# model is missing 7 observations from wave 2?
  si_all_unadj<-glmer.nb(mean_mvpa_sd~ stringencyIndex + (1|interact_id),
                         data=sd_valid[sd_valid$wave_id=="wave 2",]) 
  # summary(si_all_unadj)
```

@@

**Model**
```{r,warning=FALSE}
  si_all_cov_fully<-glmer.nb(mean_mvpa_sd~ stringencyIndex + wear + city_id + 
                          mean_temp + total_precip + 
                          age_cat + 
                          gender + 
                          children + 
                          employment + 
                          (1|interact_id),
                          data=sd_valid[sd_valid$gender!="other" & sd_valid$age_cat!="missing" &
                                     sd_valid$wave_id=="wave 2",])
```

@@

**Objective 1**

@@

Unadjusted model (all person-days with 600+ minutes of wear time)
```{r}
length(sd_valid$date)
table(sd_valid$wave_id)
```

Adjusted model (complete case; no missing data for confounders)
```{r}
# models adjusted for wave_id + city_id + wearRS + age_cat + employment + income + mean_temp + total_precip -- no missing data for wave_id, city_id, employment status, income... look for number of missing for each of the remaining variables

@@

**Sensitivity analysis 1**

@@

Adjusted
```{r}
summary(sd_valid_both$age_cat)
summary(sd_valid_both$mean_temp)
summary(sd_valid_both$total_precip)
```

**Sensitivity analysis 2**

@@

Adjusted
```{r}
summary(sens_valid$age_cat) # don't need to check for missingness in weather data since we aren't controlling for weather in this model
```

**Objective 2**

@@

Adjusted model (complete case; no missing data for confounders)
```{r}
summary(sd_valid[sd_valid$wave_id=="wave 2",]$mean_temp)
```
